Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-05 docs/evol.tex
minor fixes and adoption of Spearman correlation

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from two pairs involving the {\it Security High}
category. In general, the {\it Security High} category showed the
weakest correlations with the other categories. Our results show that
in general bugs do flock together. We do not find projects with only a
certain kind of bug; bugs come upon projects in swarms of different
kinds. Bugs of the {\it Security High} category, though, are
different: they are either not associated with other bugs, or only
weakly so. Perhaps it takes a special kind of blunder to make it a
security hazard.

\begin{table}
    \centering
    \caption{Correlation matrix}
    \label{tbl:corrmatrix}
    \input{corrmatrix.tex}
    \small The matrix presents pairwise correlations between the
        following bug categories in order: Security High, Security
        Low, Style, Bad Practice, Correctness, {\sc mt} Correctness,
        Performance, i18n, Experimental.
\end{table}

>>>>

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant, but not always
strong, correlations between all pairs. In general, the {\it Security
  High} category showed the weakest correlations with the other
categories. Our results show that in general bugs do flock together.
We do not find projects with only a certain kind of bug; bugs come
upon projects in swarms of different kinds. Bugs of the {\it Security
  High} category, though, are different: they are either not
associated with other bugs, or only weakly so. Perhaps it takes a
special kind of blunder to make it a security hazard.

\begin{table}
    \centering
    \caption{Correlation matrix}
    \label{tbl:corrmatrix}
    \input{corrmatrix.tex}
    \\
    \small The matrix presents pairwise correlations between the
        different bug categories.
\end{table}
